Is statistical significance a thing?

### 2018-02-28 doc.tex
Update doc.tex

\begin{framed}
\begin{tabular}{p{7.5cm}p{7.5cm}}
     Language in published journal articles & Rewritten using the language of ``clarity'' \\
     	\hline
        \\
     \multicolumn{2}{c}{$\mathbf{p > 0.05 \neq}$ \textbf{zero effect}} \\
        Cadmium bioaccumulates after acute exposure but has no effect on locomotion or shelter-seeking behaviour in the
        invasive green shore crab & Cadmium bioaccumulates after acute exposure but its effect on locomotion or shelter-seeking 
        behaviour in the invasive green shore crab was statistically unclear \\ 
        \\
        No effect of elevated carbon dioxide on reproductive behaviors in the three-spined stickleback & The effect of elevated 
        carbon dioxide on reproductive behaviors in the three-spined stickleback was statistically unclear \\
        \\
        The finding that bee species richness showed no significant relationship with the area of semi-natural habitat is 
        surprising because bee species richness is usually more strongly influenced by landscape context than pollination. & 
        Bee species richness is often found to be more strongly influenced by landscape context than pollination; however, 
        in the present study the relationship between bee species richness and area of semi-natural habitat was statistically 
        unclear \\ 
        \\
     \multicolumn{2}{c}{\textbf{P~values $\mathbf{> 0.05}$ should not be compared as evidence for anything}} \\
        ...yielded nonsignificant differences on measures of those skills with P values of at least 0.2, and most in the
        $0.7 \leq P \leq 0.9$ range. & ...the differences between skills developed in treatment and control individuals
        were not statistically clear ($p > 0.05$) \\
        \\
     \multicolumn{2}{c}{\textbf{The difference between ``clear'' and ``not clear'' is ``not clear''}} \\
        Substrate choice correlated significantly with food choice in males $(r_{s} = 0.32, N = 44, P < 0.05)$ but not in
        females $(r_{s} = 0.32, N = 24, NS)$. ... The authors discuss the biological reasons why there is a relationship 
        between these variables in males, but not in females & Substrate choice was positively correlated with food choice in 
        males $(r_{s} = 0.32, N = 44, P < 0.05)$, but this relationship was not statistically clear in females $(r_{s} = 0.32,
        N = 24, NS)$. A biological description comparing the correlation in males vs females is inappropriate without a direct
        test (in this case with the exact same correlation estimate, this is not a sensible test). \\
\end{tabular}
\end{framed}
   \captionof{table}{Rewriting misinformed language in the published literature using our proposed updated language.}

>>>>

\begin{tabular}{p{7.5cm}p{7.5cm}}
     Language in published journal articles & Rewritten using the language of ``clarity'' \\
     	\hline
        \\
     \multicolumn{2}{c}{$\mathbf{p > 0.05 \neq}$ \textbf{zero effect}} \\
        Cadmium bioaccumulates after acute exposure but has no effect on locomotion or shelter-seeking behaviour in the
        invasive green shore crab & Cadmium bioaccumulates after acute exposure but its effect on locomotion or shelter-seeking 
        behaviour in the invasive green shore crab was statistically unclear \\ 
        \\
        No effect of elevated carbon dioxide on reproductive behaviors in the three-spined stickleback & The effect of elevated 
        carbon dioxide on reproductive behaviors in the three-spined stickleback was statistically unclear \\
        \\
        The finding that bee species richness showed no significant relationship with the area of semi-natural habitat is 
        surprising because bee species richness is usually more strongly influenced by landscape context than pollination. & 
        Bee species richness is often found to be more strongly influenced by landscape context than pollination; however, 
        in the present study the relationship between bee species richness and area of semi-natural habitat was statistically 
        unclear \\ 
        \\
     \multicolumn{2}{c}{\textbf{P~values $\mathbf{> 0.05}$ should not be compared as evidence for anything}} \\
        ...yielded nonsignificant differences on measures of those skills with P values of at least 0.2, and most in the
        $0.7 \leq P \leq 0.9$ range. & ...the differences between skills developed in treatment and control individuals
        were not statistically clear ($p > 0.05$) \\
        \\
     \multicolumn{2}{c}{\textbf{The difference between ``clear'' and ``not clear'' is ``not clear''}} \\
        Substrate choice correlated significantly with food choice in males $(r_{s} = 0.32, N = 44, P < 0.05)$ but not in
        females $(r_{s} = 0.32, N = 24, NS)$. ... The authors discuss the biological reasons why there is a relationship 
        between these variables in males, but not in females & 
        Substrate choice was positively correlated with food choice in males $(r_{s} = 0.32, N = 44, P < 0.05)$, but this
        relationship was not statistically clear in females $(r_{s} = 0.32, N = 24, NS)$. A biological description comparing 
        the correlation in males vs females is inappropriate without a direct test (in this case with the exact same 
        correlation estimate, this is not a sensible test). \\
        \\
        ...risk of low BMD [bone mineral density] remained greater in HCV-coinfected women versus women with HIV alone
        (adjusted OR 2.99, 95\% CI 1.33–6.74), but no association was found between HCV coinfection and low BMD in men 
        (adjusted OR 1.26, 95\% CI 0.75–2.10). ... While the authors do not directly compare men and women they do state: 
        The precise mechanisms for the association between viral hepatitis and low BMD in HIV-infected women but not men 
        remain unclear. & 
        ..risk of low BMD [bone mineral density] remained greater in HCV-coinfected women versus women with HIV alone
        (adjusted OR 2.99, 95\% CI 1.33–6.74), but the association between HCV coinfection and low BMD in men was not
        statistically clear (adjusted OR 1.26, 95\% CI 0.75–2.10). ... Pursuing the biological importance of HIV on BMD in 
        women and not men is premature given these statistics and requires further study.
        \\
\end{tabular}
   \captionof{table}{Rewriting misinformed language in the published literature using our proposed updated language.}
